Testing atlantisom: true biomass output from Atlantis

### 2019-04-29 TrueBioTest.Rmd
live date

---
title: "Testing atlantisom: true biomass output from Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "April 25, 2019"
output: html_document
---

@@

Note: on Sarah's laptop, CCA took ~40 minutes to return from `run_truth` and NOBA took an hour and 26 minutes to return. Therefore, reading the RData file in as below is advised after the first run to make the plots comparing systems later in this document.

@@

```{r surveyBbased, eval = FALSE}

>>>>

---
title: "Testing atlantisom: true biomass output from Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

Note: on Sarah's laptop, CCA took ~40 minutes to return from `run_truth` and NOBA took an hour and 26 minutes to return. Therefore, reading the .RData file in as below is advised after the first run to make the plots comparing systems later in this document.

@@

```{r surveyBbased}
